How to obtain the redshift distribution from probabilistic redshift estimates

### 2017-06-13 research/paper/draft-editing.tex
saving this for now

The directed acyclic graph of Fig. \ref{fig:pgm} represents a probabilistic graphical model for hierarchical inference of $n(z)$, the mathematical interpretation of which will be presented below.

\begin{figure}
	\begin{center}
		\includegraphics[width=0.5\textwidth]{pgm.png}
		\caption{\textbf{Replace \texttt{daft} version with more polished \texttt{tikz} version.}}
%		\caption{This directed acyclic graph corresponds to a PGM for a hierarchical inference of $p(\vec{\theta}|\{\vec{d}_{i}\})$.  In this graph, all random variables are shown in circles, with observed random variables shown in shaded circles.  Relationships between variables are indicated by arrows from parameters to the variables distributed according to functions of them.  The box indicates that there are a number of copies of the relationships between boxed parameters, each independent of all others.  The hyperparameters $\vec{\theta}$ representing $n(z)$ are at the top.  Independently drawn from a function of the hyperparameters $\vec{\theta}$ are galaxy redshifts $\{z_{i}\}$ below.  The observed galaxy photometry $\{\vec{d}_{i}\}$, shown in shaded circles, is determined by the redshifts above.}
	\label{fig:pgm}
	\end{center}
\end{figure}

\textbf{Math from \texttt{prob-z} version will go here.}

>>>>

We present the two attributes of a probabilistic graphical model (PGM) for the redshift distribution $n(z)$: the directed acyclic graph of Fig. \ref{fig:pgm} and its mathematical interpretation below.  The assumption underlying the concept of photo-$z$ estimation is that each galaxy $i$ has some observed photometric data $\vec{d}_{i}$ (fluxes, magnitudes, or colors) that is drawn from a function of its redshift $z_{i}$, which is a parameter in this model.  The redshifts $\{z_{i}\}$ for all galaxies in a survey are random draws from the redshift distribution, a function which itself may be parametrized by hyperparameters comprising $\vec{\phi}$ that are shared among all $N$ galaxies in the survey.  From this perspective, $n(z)$ is itself a probability distribution for galaxy redshifts, i.e. $z_{i} \sim n(z)$.  Given a functional form of $n(z)$, we can say $n(z) = p(z_{i}|\vec{\phi})$ for any $i = 1, \dots, N$, determining that $n(z)$ is itself a likelihood.  This PGM enables hierarchical Bayesian inference; we will directly infer the posterior probability distribution $p(\vec{\phi} | \{\vec{d}_{i}\})$ of $\vec{\phi}$ given the observations.

\begin{figure}
	\begin{center}
		\includegraphics[width=0.5\textwidth]{pgm.png}
		\caption{This directed acyclic graph corresponds to a PGM for a hierarchical inference of $p(\vec{\phi}|\{\vec{d}_{i}\})$.  In this graph, all random variables are shown in circles, with observed random variables shown in shaded circles.  Relationships between variables are indicated by arrows from parameters to the variables distributed according to functions of them.  The box indicates that there are a number of copies of the relationships between boxed parameters, each independent of all others.  The hyperparameters comprising $\vec{\phi}$, which define $n(z)$, are at the top.  Independently drawn from a function of the hyperparameters $\vec{\phi}$ are galaxy redshifts $\{z_{i}\}$ below.  The observed galaxy photometry $\{\vec{d}_{i}\}$, shown in shaded circles, is determined by the redshifts above.}
	\label{fig:pgm}
	\end{center}
\end{figure}
